\documentclass[12pt]{article}

\usepackage[letterpaper]{geometry}
\usepackage{times}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}


\usepackage{setspace}
\doublespacing

\begin{document}
\begin{flushleft}
\begin{center}
\textbf{Klamath}
\end{center}

\setlength{\parindent}{0.5in}

Klamath is an IWAD built for the Doom Engine. It revolves around the titular Klamath character fighting an evil corporation and its masters, and involves themes of urban warfare and fast-paced gunplay.  The goal is to take what's possible with the Vanilla DOOM Engine and create a more punchy experience using DeHacKeD.

\textbf{1). Playing the Game}

Klamath is just a WAD that requires a variant of the Doom Engine to play. This guide personally recommends GZDoom, as it is one of the most technologically advanced Doom source-ports and allows for easy modification of the game. However, Klamath should be compatible with any DeHacKeD-compatible source port, which includes the original Doom Engine from 1994.

\textbf{1.1). MBF-Compatible Source Port}

The DeHacKeD code is included as a lump in the Klamath WAD that an MBF-compatible engine can load automatically. Feel free to ignore the "klamath.deh" file, and run the following command:

"gzdoom -iwad klamath.wad"

Where "gzdoom" is the path to your executable, e.g. "gzdoom" or "prboom-plus".

\textbf{1.2). Chocolate/Crispy Doom}

Chocolate and Crispy Doom allow one to load DeHacKeD patches via a command line. If you want a more purist experience, run the following command:

"chocolate-doom -iwad klamath.wad -deh klamath.deh"

Replace "chocolate-doom" with the path to your Chocolate/Crispy Doom executable.

\textbf{1.3). Vanilla Doom}

If you just really want to run Klamath on the original Doom Engine, you first need to apply the DeHacKeD patch. Download the original DeHacKeD program, apply the patch, and run the Doom Engine using klamath.wad as the IWAD.

\textbf{2). The Story}

The year is 2020. Sixty years ago, Earth was invaded by aliens. Fifty-nine years ago, Earth was invaded again by aliens while the first alien invasion was still going on. Five poorly-scheduled alien invasions later, the resulting standoff lead to an uneasy truce, where they kind of agreed that everyone got the planet. A few decades later, mingling and interbreeding between the alien races and the humans have essentially integrated them into Earth's population.

You are Klamath, a private eye doing some investigation into the Zirconium Corporation, the world's leading producer of military-grade weapons, run by the Metal People. You have a hunch that they're doing something dastardlty. After digging through a few dumpsters, you find some documents that prove your hunch correct. They're building the Hummingbird Engine, a weapon of mass destruction intended to remove the non-Metal People from Earth, violently, by summoning some kind of army.

You go to the police and tell them about your findings, but they lock you up in the drunk tank. You guess you came across as a bit of a mess, given that they revoked your PI license after your last "hunch" led to the mall having to close down, so you decide to bide your time. However, you overhear the cops talking about you:

"So, what're we gonna do with Klamath?"

"Fry him. He knows too much about our little project."

"Aye aye."

Realizing that you've stumbled onto a conspiracy, you draw your pistol from a hidden compartment in your coat, shoot off the lock to your cell, and grab the nearest fire axe. As you ready yourself for a brawl, you hear the air sirens outside. A brief look tells you two things: the military has you surrounded, and your day's about to get a whole lot more bloody.

The documents you found indicated that the Zirconium Corporation intends to activate the Hummingbird Engine at 9 'o' clock PM. If they manage that, the death toll will be in the tens of billions. It's up to you to fight past the military, the police force, Zirconium's forces, and whatever else they can summon in order to save the world from utter destruction.

\textbf{3). The Weapons}

Klamath will wield a variety of weapons during his journey. They are enumerated below.

\textbf{3.1). The Fire Axe}

A melee weapon for when you've exhausted all other options. The Reno Fire Code says all buildings must have at least one fire axe, just in case there's a fire, so you should never be without this weapon. Fires slowly and does low damage, unless boosted with Steroids.

\textbf{3.2). The Pistol}

Your trusty pistol. You have it stowed away in a secret compartment of your coat, so even if you take a beating you'll still be able to take it out. Fires moderately quickly, but does low damage.

\textbf{3.3). The Sawed-Off}

The sawed-off shotgun is truly a weapon for the scrappy. It fires moderately quickly in a spread pattern that does more damage than the pistol. Useful for taking out large numbers of low-tier enemies.

\textbf{3.4). The Submachine Gun}

A military-grade submachine gun, essentially a box that bullets come out of. Fires very quickly and does high damage, but will blow through your ammo very quickly. Useful in tight spaces when you're surrounded, and have no choice but to spray and pray.

\textbf{3.5). The Scorcher}

A makeshift flamethrower that expels gasoline into a fire source to produce a napalm-like attack. Fires slowly and has a small range, but does a high amount of damage.

\textbf{3.6). The Double-Barrel}

This is a double-barrelled murder machine guaranteed to leave no enemy left standing. It makes up for its slow fire rate with an extremely high damage output. Useful for taking down bulkier enemies.

\textbf{3.7). The Rocket Launcher}

The original death-cannon, capable of firing devastating explosive rockets. Fires moderately quickly and has a high damage output, but ammo for it is usually scarce. Cuts through large numbers of low-tier enemies like butter, and can take down high-tier enemies quickly.

\textbf{3.8). The Flamethrower}

A gasoline-powered flamethrower capable of spitting dangerously high amounts of firey death. Fires quickly and does high amounts of damage, but runs through the gasoline supply very quickly. This legendary weapon makes even the strongest monsters check their closets at night.

\textbf{3.9). The Hunting Rifle}

A high-power sniper weapon for hunting monsters. Can deal high amounts of damage over a long range, but takes a long time to reload. Useful for picking off enemies from a distance.

\textbf{4). The Enemies}

Zirconium Corporation has ties to the police, the military, and the monsters trapped in the underworld (for now). Each and every one will do the best to see you dead.

\textbf{4.1). The Police Officer}

The police officer is a low-level grunt, a human in a world where human's aren't hot shit anymore. Wields a pistol, and dies in 2-3 pistol shots or 1-2 shotgun blasts. Only a problem in large numbers.

\textbf{4.2). The Military Private}

This crocodile is dead-set on making sure you don't complete your mission. Wields a shotgun that can take you by surprise if you aren't ready for it. Is only slightly bulkier than the Police Officer.

\textbf{4.3). The Robot}

A police robot that they send after dangerous criminals. Can take quite a bit of punishment, but only has a melee attack. Keep your distance and you'll be golden.

\textbf{4.4). B.P.G.}

The Big Plasma Gunner wields an experimental plasma gun that cuts through even the sturdiest defenses. However, they can't stand up to the classic shotgun-to-the-face treatment.

\textbf{4.5). Mechasuit}

They only deploy these things when the going starts getting rough. Carries an honest-to-god cannon that rapidfires dangerous cannonballs. Deploys explosives charges if you get too close to him. Will take quite a bit of punishment before going down; truly a high-priority target.

\textbf{4.6). Plasma Corporals}

The Butterfly People of Sigma-9 brought their experimental plasma technology to Earth, and they're by far the best at using it. Their plasma suit will pepper you with projectiles from far away, and they're armed with the dangerous plasma sword that'll cut right through your armor. Thankfully, they're more lightweight than the other higher-tier enemies, and two double-barrel blasts should take them out for the count.

\textbf{4.7). Seagull}

Experimental brain implants have turned these birds into dangerous missiles. Will dive-bomb at you unless you shoot them to stop them. They're birds, so it should only take a couple of shots from the pistol to turn them into corpses.

\textbf{4.8). Turtle Commando}

Navy SEALs? Try Navy TURTLEs. This highly-trained operate carries a missile weapon capable of blowing your nosey ass to smithereens. In addition, their thick shell means taking them out is easier said than done. A menace to society at long range, but can't take the heat of the flamethrower.

\textbf{4.9). Cubic Beings}

The Cubic Beings of Eta-21 have sided with the Zirconium Corporation, for some reason. Bulky as all hell, and their fire blast attack can tear through you in mere milliseconds. Long-range attacks like rockets and the hunting rifle can round them out.

\textbf{4.10). General Zinc}

When asked whether or not the fact that he commanded the army and was the CEO of the Zirconium Corporation was an instance of corruption, he got the reporter court-marshalled. With his abs of steel, it's going to take concentrated fire to truly do him in. Wields two rocket launchers, good luck dodging his attacks. Keeps crawling his way up from Hell.

\textbf{4.11). Apparition}

The soldiers of the army the Zirconium Corporation is trying to summon. Takes between two and three double-barrel blasts, and fires a dangerous energy shot. Bring the Flamethrower to deal with large numbers.

\textbf{4.12). Possessed}

A lost soul corrupted beyond recognition by the Apparitions. Their skin has hardened to deflect bullets, making them extremely difficult to kill. Persistent fire from the double-barrel shotgun or the rocket launcher can destroy them.

\textbf{4.13). Ghast Summoner}

A special type of Apparition that summons Seagulls. Annoying as all hell; make them a priority target if you don't like dealing with bird shit.

\textbf{4.14). King Commander}

The big boss of the Apparitions, and the leader of the force planning to invade Earth. His deadly posession attack will end your journey. Will also use his infernal magic to summon the enemies you've already faced. Give him everything you've got; the fate of the world depends on it.

\textbf{5). License}

This work is licensed under a Creative Commons Attribution-ShareAlike International 4.0 License.
\end{flushleft}
\end{document}